#Problem Defination
Kira Plastinina is a Russian brand that is sold through a defunct chain of retail stores in Russia, Ukraine, Kazakhstan, Belarus, China, Philippines, and Armenia. The brand’s Sales and Marketing team would like to understand their customer’s behavior from data that they have collected over the past year. More specifically, they would like to learn the characteristics of customer groups.

#Data Sourcing
[http://bit.ly/EcommerceCustomersDataset -This is where our data is collected from.


#Check the Data

#library importation.

```{r}
install.packages("readr", dependencies=TRUE, INSTALL_opts = c('--no-lock'))
install.packages("tidyverse")
```
```{r}
library("tidyverse")
```



```{r}
library(tidyverse)
library(grid)
library(devtools)

```

```{r}
#loading the dataset
data2=read.csv('http://bit.ly/EcommerceCustomersDataset')
data2
```

```{r}
head(data2)
```

```{r}
#check datatypes
str(data2)
```

```{r}

# Changing the type of the loaded dataset to a dataframe
data2= as.data.frame(data2)

# Cleaning column names, by making them uniform
colnames(data2) = tolower(colnames(data2))
data2
```
```{r}

# Previewing some statistical summaries of the dataset
summary(data2)
```

```{r}

# Checking the shape of the dataframe
dim(data2)
```
```{r}
# Checking for duplicated data
anyDuplicated(data2)
#our data has 159 duplicated values
```

```{r}
#drop duplicates
install.packages("dplyr")
library(dplyr) 

data2 = distinct(data2)

# Ckecking whether the duplicates have been successfully dropped
anyDuplicated(data2)
```

```{r}

# Checking for missing values
colSums(is.na(data2))
```

```{r}
# Dropping missing values
data2= na.omit(data2)
```

```{r}
is.na(data2)
```

```{r}

cat_cols = c('month', 'operatingsystems',	'browser',	'region',	'traffictype', 'visitortype')

# Changing columns to factors
for( i in cat_cols){
   data2[,i] = as.factor(data2[,i])
}

```
```{r}

# Checking the structure of the cleaned dataframe
str(data2)
```

```{r}
#check for outliers
install.packages("ggplot2")
library("ggplot2")


options(repr.plot.width = 11, repr.plot.height = 5)
ggplot(data2, aes(month, productrelated, col = weekend)) + 
  geom_boxplot() + 
  labs(x = 'Month', y = 'Product related', title = 'Checking outliers in the product related feature') + 
  theme(legend.position = 'top', legend.text = element_text(size = 10),
       plot.title = element_text(size = 11, color = 'darkmagenta', face = 'bold'))
```
```{r}
# Plotting boxplots to check for outliers
options(repr.plot.width = 7, repr.plot.height = 5)
ggplot(data2, aes(visitortype, productrelated, col = revenue)) + 
  geom_boxplot() + 
  labs(x = 'Visitor type', y = 'Product related', title = 'Checking outliers in the product related feature per visitor type') +
  scale_color_brewer(palette = 'Set1') +
  theme(legend.position = 'top',
       plot.title = element_text(size = 11, color = 'darkmagenta', face ='bold'))
```



```{r}
#check for outliers
  boxplot(administrative~revenue,data=data2)
```
```{r}
  boxplot(administrative_duration~revenue,data=data2)
```
```{r}
 boxplot(informational_duration~revenue,data=data2)
```
```{r}
 boxplot(productrelated~revenue,data=data2)
```
#DISTRIBUTION PLOTS
```{r}
# Plotting density plots to check for distributions
options(repr.plot.width = 11, repr.plot.height = 5)
p1 = ggplot(data2, aes(productrelated, col = revenue)) + 
  geom_density(aes(fill = revenue), alpha = 0.4) + 
  labs(x = 'Product related', y = 'Density', title = '') + 
  theme(legend.position = 'none', 
       plot.title = element_text(size = 12)) 
p1
```
```{r}
#univariate analysis
hist(data2$administrative, 
     main="Histogram for administrative", 
     xlab="administrative", 
     border="black", 
     col="green")
```

```{r}
hist(data2$productrelated, 
     main="Histogram for productrelation", 
     xlab=" productrelation", 
     border="black", 
     col="green")
```
```{r}
hist(data2$bouncerates, 
     main="Histogram for bouncerates ", 
     xlab="bouncerates ", 
     border="black", 
     col="gold")
```

```{r}

p2 = ggplot(data2, aes(bouncerates, col = revenue)) + 
  geom_density(aes(fill = revenue), alpha = 0.4) + 
  labs(x = 'Bouncerates', y = '', title = '') + 
  theme(legend.position = 'top') 
p2
```
```{r}
p3 = ggplot(data2, aes(exitrates, col = revenue)) + 
  geom_density(aes(fill = revenue), alpha = 0.4) + 
  labs(x = 'exitrates', y = '', title = '') + 
  theme(legend.position = 'none', 
       plot.title = element_text(size = 12)) 
p3
```
```{r}
p4 = ggplot(data2, aes(exitrates , col = revenue)) + 
  geom_density(aes(fill = revenue), alpha = 0.4) + 
  labs(x = 'exitrates ', y = '', title = '') + 
  theme(legend.position = 'top') 
p4
```

#scatter plots

```{r}
library(ggplot2)
options(repr.plot.width = 11, repr.plot.height = 5)

p1 = ggplot(df, aes(productrelated, productrelated_duration, col = revenue)) + 
    geom_point() + theme(legend.position = 'none') + 
    labs(x='Product related', y ='Product related duration')
p1
```
```{r}
p2 = ggplot(data2, aes(administrative, administrative_duration, col = revenue)) +
    geom_point() + theme(legend.position = 'none') +
    labs(x = 'Administrative', y = 'Administrative duration')
p2
```

```{r}
p3 = ggplot(data2, aes(informational, informational_duration, col = revenue)) + 
    geom_point() + theme(legend.position = 'none') + 
    labs(x = 'Informational', y = 'Informational duration')
p3
```
```{r}
p4 = ggplot(data2, aes(pagevalues,	specialday	, col = revenue)) + geom_point() + theme(legend.position = 'none') +
    labs(x = 'Page values', y = 'Special day')
p4
```
```{r}
p1 = ggplot(data2, aes(productrelated, productrelated_duration, col = revenue)) + 
    geom_point() + theme(legend.position = 'none') + 
    labs(x='Product related', y ='Product related duration')
p1
```
#HEATMAP
```{r}

# Plotting a correlogram to check for correlations
library(dplyr)
install.packages("ggcorrplot")
library(ggcorrplot)
options(repr.plot.width = 4, repr.plot.height = 5)

corr = round(cor(select_if(data2, is.numeric)), 2)
ggcorrplot(corr, hc.order = T, ggtheme = ggplot2::theme_gray,
   colors = c("#6D9EC1", "white", "#E46726"), lab = F)
```
#encode  categorical variables
```{r}
# Creating a copy of the cleaned dataframe
non_dummy_df = data.table::copy(data2)

# Encoding categorical variables
month = data.frame(model.matrix(~0+data2$month))
opr = data.frame(model.matrix(~0+data2$operatingsystems))
brw = data.frame(model.matrix(~0+data2$browser))
reg = data.frame(model.matrix(~0+data2$region))
trf = data.frame(model.matrix(~0+data2$traffictype))
vis = data.frame(model.matrix(~0+data2$visitortype))
wkn = data.frame(model.matrix(~0+data2$weekend))
rev = data.frame(model.matrix(~0+data2$revenue))

# Dropping columns which have already encoded
drop_cols = c('month', 'operatingsystems',	'browser',	'region',	'traffictype', 'visitortype', 'weekend', 'revenue')
data2= select(data.frame(cbind(data2, month, opr, brw, reg, trf, vis, wkn, rev)), -drop_cols)
```
```{r}
main_df = data.table::copy(data2)

# Normalising the data
data2 = as.data.frame(apply(data2, 2,  function(x) (x - min(x))/max(x) - min(x)))
```

```{r}
# Performing clustering with the optimal number of clusters
kmeans_res = kmeans(data2, 4)

# Checking the cluster centers of each variable
kmeans_res$centers
```

```{r}
# Previewing the size of observations in each cluster
kmeans_res$size
```
```{r}
# Checking how some features have been clustered
options(repr.plot.width = 11, repr.plot.height = 6)

p1 = ggplot(data2, aes(productrelated, productrelated_duration, col = kmeans_res$cluster)) + 
    geom_point() + theme(legend.position = 'none') + 
    labs(x='Product related', y ='Product related duration')
p1
```
```{r}
p2 = ggplot(data2, aes(administrative, administrative_duration, col = kmeans_res$cluster)) +
    geom_point() + theme(legend.position = 'none') +
    labs(x = 'Administrative', y = 'Administrative duration')
p2

```
